The title

### 2024-10-22 05_Manuscript/manuscript.Rmd
updating efa results

```

@@

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML1 >= .30 & ML2 >= .30, "no", "no"
      )
    )
  )) %>% 
  mutate(question = rownames(.))

## Make a dataframe with loadings and item text
model1_loadings <- efa_loadings_2
model1_loadings$ItemNum <- row.names(model1_loadings)
model1_withtext <- merge(item_text, model1_loadings, by = 'ItemNum')

```

@@

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML3 >= .30, "yes", "no"
        )
      )
    )
  ) %>% 
  mutate(question = rownames(.)) %>% 
  mutate(
    keep = ifelse(
          (ML1 >= .30 & ML2 >= .30) | 
            (ML1 >= .30 & ML3 >= .30) |
            (ML3 >= .30 & ML2 >= .30), "no", keep
          )
  )

model2_loadings <- efa_loadings_2
model2_loadings$ItemNum <- row.names(model2_loadings)
model2_withtext <- merge(item_text, model2_loadings, by = 'ItemNum')
```

@@

efa_loadings_3 <- as.data.frame(unclass(EFA_fit_3$loadings)) %>% 
  mutate(question = rownames(.)) %>% 
  rowwise() %>%
  mutate(keep = sum(c_across(-question) >= .30)) %>% 
  ungroup()

model3_loadings <- efa_loadings_3
model3_loadings$ItemNum <- model3_loadings$question
model3_withtext <- merge(item_text, model3_loadings, by = 'ItemNum')

```

-   take the final version of each "best model"
-   get down to 5 items each or whatever is left (best loading and
    theoretical)
-   look at the fit indices to tell which may be best

>>>>

questions <- import("../03_Data/questions.xlsx")
```

@@

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML1 >= .30 & ML2 >= .30, "no", "no"
      )
    )
  )) %>% 
  mutate(question = rownames(.)) %>% 
  left_join(questions,
            by = c("question" = "Question_Number")) %>% 
  arrange(desc(ML1)) %>% 
  export(., "results/2_factor.xlsx", row.names = F)
```

@@

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML3 >= .30, "yes", "no"
        )
      )
    )
  ) %>% 
  mutate(question = rownames(.)) %>% 
  mutate(
    keep = ifelse(
          (ML1 >= .30 & ML2 >= .30) | 
            (ML1 >= .30 & ML3 >= .30) |
            (ML3 >= .30 & ML2 >= .30), "no", keep
          )
  ) %>% 
  left_join(questions,
            by = c("question" = "Question_Number")) %>% 
  arrange(desc(ML1)) %>% 
  export(., "results/3_factor.xlsx", row.names = F)
```

@@

efa_loadings_3 <- as.data.frame(unclass(EFA_fit_3$loadings)) %>% 
  mutate(question = rownames(.)) %>% 
  rowwise() %>%
  mutate(keep = sum(c_across(-question) >= .30)) %>% 
  ungroup() %>% 
  left_join(questions,
            by = c("question" = "Question_Number")) %>% 
  arrange(desc(ML1)) %>% 
  export(., "results/5_factor.xlsx", row.names = F)
```

- import the edited files and test those models for fit 
- theory is 5, so if the fit is similar, then go with five

--- 
test cfa 
test MGCFA --> use new package to include information 
---
